---
title: "final"
author: "Laith Alayassa"
date: "6/28/2021"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)     # for data cleaning and plotting
library(lubridate)     # for date manipulation
library(ggthemes)      # for more themes (including theme_map())
library(plotly)        # for the ggplotly() - basic interactivity
library(gganimate)     # for adding animation layers to ggplots
library(readr)
library(gt)            # for creating nice tables
theme_set(theme_minimal())
library(readxl)
library(ggbump)

```


I have lived in Armenia for the past two years (2018-2020) before coming back here to Palestine, there, I have finished my IB diploma and lived in an international school at times, and finished the two years living with locals. When I first came to Armenia, I did not feel it was very different from my home in Palestine, they were both countries with poor populations, however, there was a noticeable difference in the economic and social situation in Armenia after those two years have passed, and I want to investigate.

In 2019, Armenians around me were laughing at the fact that their country was marked as the angriest in the world in a Gallup survey with %45 of their population expressing feeling a lot of anger in the previous day (McCarthy). This got me thinking about the well-being and the happiness of the population since I imagine that a psychologically distressed population would have a hard time developing its economy.

```{r}
#Source: (“World Happiness Index - Knoema.Com”)
hapiness_index <- read_excel("Armenian_Data/hapiness_index.xlsx") %>% 
  pivot_longer( cols = starts_with("20"), names_to = "year") 
```

```{r}
hapiness_index %>% 
  ggplot(aes(x = year,
             y = value,
             group = 1)) +
  geom_point() +
  geom_line()

```

We can see that during the past few years starting from 2017, there has been a sharp increase in the happiness index in the country compared with the prior years. This increase of nearly 1 point in hapiness scale took Armenia from being the 128th happiest country to the 86th happiest country in the world in an extraordinarly short time(“World Happiness Index - Knoema.Com”).

These conflicting messages suggest that while Armenians might be the angriest people on the planet -however extraordinary generous- they are making rapid progress in terns if happiness.

I will try to explore the reasons for this increase in happiness and overall well-being of the country that I have witnessed in such a short time and that the data suggests.

